Data Analysis of Mental Health Trends from 2014 to 2023 in Toronto

### 2024-01-25 outputs/paper/paper.qmd
completed some references

Raw data downloaded from City of Toronto's open data includes 25 data features (see @tbl-raw for each data feature and its content), many of which are not important in this analysis. Therefore, this report will not explain each of the data feature; details can be found [@citeMentalData]. The raw dataset includes 105821 data entries. Some data cleaning is performed. First, relevant data features are selected for analysis (occurred year, sex, age group, and premise types). Then data is cleaned by renaming the variables, so that their names are obvious. The variable names are as follows:

@@

Moreover, there are certain entries containing the value "Not Recorded," which are removed to ensure the reliability and accuracy of the dataset. After data pre-processing, there are 104530 data entries, each with 4 features described above. A Data overview is provided in the next section to further display the data.

@@

```{r fig.align='center'}
#| echo: FALSE
#| message: FALSE
#| label: fig-premise_type
#| fig-cap: Percentage of MHA apprehensions by premises type

>>>>

Raw data downloaded from City of Toronto's open data includes 25 data features (see @tbl-raw for each data feature and its content), many of which are not important in this analysis. Therefore, this report will not explain each of the data feature; details can be found [@citeMentalData]. The raw dataset includes 105821 data entries. Some data cleaning is performed. First, relevant data features are selected for analysis (OCC_YEAR: occurred year, SEX: sex, AGE_COHORT: age group, and PREMISES_TYPE: premise types). Then data is cleaned by renaming the variables, so that their names are obvious. The variable names are as follows:

@@

Moreover, there are certain entries containing the value "Not Recorded," which are removed to ensure the reliability and accuracy of the dataset. After data pre-processing, there are 104530 data entries, each with 4 features described above. A data overview is provided in the next section to further display the data.

@@

```{r fig.align='center'}
#| echo: FALSE
#| message: FALSE
#| label: fig-premise_type
#| fig-cap: Percentage of MHA apprehensions by premise types
